Differential Expression - Dx

### 2020-04-07 cmc-rnaseq-de/Differential-Expression_Dx.Rmd
fix knit to folder entity

---
title: "Differential Expression"
author: "Kelsey Montgomery, Gabriel Hoffman, Thaneer Perumal"
date: "`r date()`"
output: html_document
---

@@

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/Differential-Expression.Rmd",
                                 parentId ="syn21859863",
                                 folderName = "Differential Expression - Dx")
```

>>>>

---
title: "Differential Expression - Dx"
author: "Kelsey Montgomery, Gabriel Hoffman, Thaneer Perumal"
date: "`r date()`"
output: html_document
---

@@

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/Differential-Expression_Dx.Rmd",
                                 parentId ="syn21859863",
                                 folderName = "Differential Expression - Dx")
```
